Brief Announcement: An Improved Lower Bound for Dynamic Graph Partitioning

### 2020-01-27 paper/paper.tex
undo deleting appendix

\begin{appendix}
\end{appendix}

\end{document}

>>>>

\begin{appendix}
	-
	-\section{Ommited results}
	-
	-\begin{enumerate}
		-  \item The lower bound of $\Omega(\ell)$ for the scenario with at most $(1/3-1/k)$-augmentation
		-  \item Costly cascade example (it is easy to present $k^2$ and $k\cdot \sqrt{k}$ (with different approach), and then we can combine these to obtain $k^3$)
		-  \item $k$-competitive algorithm for the ring communication pattern
		-  \item $O(\ell)$-competitive algorithm for $k=4$ and $k=5$
		-\end{enumerate}
	-
\end{appendix}
\end{document}
